A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-19 latex/main.tex
Tweaks for Acks

SHZ acknowledges support from
Oxford Population Health, University of Oxford
(NDPH Intermediate Research Fellowship)
and
% Apparently, it is now Johnson & Johnson Innovative Medicine.
Janssen Pharmaceuticals
(Oxford-Janssen Translational Genomics Fellowship).
% JK: Commenting this out until exact wording is provided. I'm pretty
% sure that "Wellcome trust" is wrong.
% IG is supported by the Wellcome trust (DPhil in Genomic Medicine and Statistics).
DSP acknowledges funding administered by the Danish National Research Foundation in support of the Pioneer Centre for SMARTbiomed. 
% "acknowledges support" here means "was awarded this grant 
% and it supported this research"
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation. For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
funding acquisition, JK;
resources, JK;
supervision, JK.

>>>>

SHZ acknowledges support from
Oxford Population Health, University of Oxford
(NDPH Intermediate Research Fellowship)
and
% Apparently, it is now Johnson & Johnson Innovative Medicine.
Janssen Pharmaceuticals
(Oxford-Janssen Translational Genomics Fellowship).
IG is supported by Wellcome (DPhil in Genomic Medicine and Statistics, 228319/Z/23/Z).
DSP acknowledges funding administered by the Danish National Research Foundation
in support of the Pioneer Centre for SMARTbiomed.
% "acknowledges support" here means "was awarded this grant 
% and it supported this research"
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation. For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

@@

% Credit system: https://credit.niso.org/
Conceptualization, SHZ, SPO, JK;
% Methods dev, software dev, and approaches
methodology, SHZ, YW, AI, KE, BJ, DSP, SPO, JK;
% Data analysis and literature review/synthesis
investigation, SHZ, YW, AI, KE, IG, SPO, JK;
writing--original draft, SHZ, JK;
writing--review \& editing, everyone;
funding acquisition, JK;
resources, JK;
supervision, JK.
